Categorical Predictor Embeddings in Actuarial Modeling

### 2021-04-03 manuscript/manuscript.Rmd
fix basic nn description

For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being sent to a hidden linear layer of 64 units. A ReLU activation,

\begin{equation}
x \mapsto \max(0, x),
\end{equation}

is then applied to the outputs before they are sent to a final output layer resulting in a scalar. To constrain
predictions to be positive, we apply softplus activation, which is defined to be

\begin{equation}
x \mapsto \log(1 + e^x). 
\end{equation}

>>>>

For Model 2, we build a feedforward neural network, whose architecture is shown in Figure \@ref(fig:nn-1). 
The categorical inputs go through one-dimensional embedding
layers where they are each mapped to a scalar. The embeddings are then concatenated with the numeric predictors, which
have been normalized in data pre-processing, before being passed through a feedforward layer (with ReLU activation)
 to obtain a scalar
value between 0 and 1, as constrained by a sigmoid output activation. This scalar output represents the proportion of
coverage amount that is paid out, so we multiply it by the unnormalized dollar amount of the coverage amount to obtain
our prediction of the claims paid.
